Freezing of a Weeks-Chandler-Anderson Fluid using classical Density Functional Theory

### 2020-12-02 papers/thesis-kirstie/thesis.tex
skeleton for beamer presentation for Kirstie
thesis-kirstie/thesis.bib

\abstract{
  We use Classical Density Functional Theory (cDFT) to predict the 
  freezing of a Weeks-Chandler-Anderson (WCA) fluid, and construct
  pressure-temperature and temperature-density phase diagrams. 
  A WCA fluid consists of soft spheres that exhibit the repulsive 
  portion of the Lennard-Jones potential widely used to model the 
  interaction of two neutral atoms. Our cDFT functional is constructed 
  using Soft Fundamental Theory (SFMT) with Tarazona's tensor expression 
  for $\Phi_3$, and Schmidt's error function model in which we have 
  incorporated our temperature dependent parameters $\alpha$ and $\Xi$. 
  We find $\Xi$ by making the second virial coefficients of the error 
  function potential and the WCA potential equal. Our functional was 
  successful in predicting the freezing of the WCA fluid with a fairly 
  good match to Monte-Carlo simulations. 
  This result suggests that SFMT may provide a strong foundation for 
  future density functionals that will model real fluids.
}

@@

SFMT is an extension of Fundamental Measure Theory (FMT)~\cite{rosenfeld1989}
that was developed for the hard-sphere fluid which can be derived from

@@

>>>>

\abstract{
  We use Classical Density Functional Theory (cDFT) to predict the 
  freezing of a Weeks-Chandler-Anderson (WCA) fluid, and construct
  pressure-temperature and temperature-density phase diagrams. 
  A WCA fluid consists of soft spheres that exhibit the repulsive 
  portion of the Lennard-Jones potential widely used to model the 
  interaction of two neutral atoms. Our cDFT functional is constructed 
  using Soft Fundamental Theory (SFMT) Schmidt's error function model 
  in which we have incorporated temperature dependent parameters to make
  %$\alpha$ and $\Xi$. We find $\Xi$ by making the second virial 
  %coefficients of the error function potential and the WCA potential equal. 
  the second virial coefficient correct. Our functional was 
  successful in predicting the freezing of the WCA fluid with a fairly 
  good match to Monte-Carlo simulations. This result suggests that SFMT 
  may provide a strong foundation for future density functionals that 
  will model real fluids.
}

@@

SFMT was developed by Schmidt~\cite{schmidt1999density, schmidt2000fluid} 
for soft-spheres, and is an extension of Fundamental Measure Theory (FMT). 
FMT was developed 
by Rosenfeld~\cite{rosenfeld1989, rosenfeld1994,fmtfromsptandsignerror}, 
for the hard-sphere fluid,
%, and which can be 
and derived from 
%by expanding 

@@

%to inhomogeneous, or non-uniform hard-sphere fluids.
